Linting Linearity in Core/System FC

### 2022-11-08 proposal.tex
Initial idea for let-recs

letrec f True = f False
       f False = x
in f True
\end{code}

Plan: make let-bound variables remember the usage environment.
See ticket #18694.

>>>>

letrec f = \case
        True -> f False
        False -> x
in f True
\end{code}

Following the idea of making let-bound variables remember the usage environment
here's an informal description that that example is well typed. We want to
anotate the let-bound variable $f$ with a usage environment delta $\delta$, and
use the binding body to compute it.

Now, how to compute the usage environment of a case expression? It's described
here if I'm not mistaken
https://gitlab.haskell.org/ghc/ghc/-/wikis/uploads/355cd9a03291a852a518b0cb42f960b4/minicore.pdf.

However, not understanding it, my take would be that we can compute the usage
environment of every branch of the case expression and make sure that they all
unify (wrt to submultiplicities). The special case is when the branch happens to
call $f$ itself while computing the usage environment of $f$. If it were another
let bound variable we'd add its own usage environment to the one we're
computing; if it were a lambda bound variable we'd add [itself $:=$ its
multiplicity].

My idea is that we can emit a special usage [$rec := p$], which, when unified
against the other case branches $\delta$ will always succeed with a unification
mapping from $rec \rightarrow p\delta$ scaled by the multiplicity of $rec$

So taking the example, to compute the usage environment of $f$, we'd compute for
the second branch $[x := 1]$ and for the first branch $[rec := 1]$. Then, we'd
unify them with $rec \rightarrow [x := 1*1]$, and somehow result in $[x := 1]$

An example which should break linearity because $x$ is not linear in the first
branch:
\begin{code}
letrec f = \case
         True -> f False + f False
         False -> x
    in f True
\end{code}

To compute the usage environment of $f$ we take the second branch usage
environment $[x := 1]$ and the first branch usage $[rec := 1+1]$ and unify them,
somehow resulting in $[x := 2]$. Now, to lint the linearity in the whole let
expression we must ensure that the body of the let uses $x$ linearly. The body
is $f True$, which is a let-bound variable (how to distinguish functions that
must be applied vs variables) so we take its usage environment $[x := 2]$ which
does not use $x$ linearly and thus breaks linearity.
